### 2020-05-22 doc/manuscript/MEE_manuscript.Rmd
update manuscript
#31

handling trees that died ([issue 31](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/31))

>>>>

Based on the findings of [Caillerete et al. 2017](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/blob/master/doc/references/Cailleret_et_al-2017-GCB.pdf), we cutcut off the records of all dead trees 20 years prior to death.
